HO unification from object language to meta language

### 2024-03-31 paper/main.tex
fix english 6

\noindent
Remark that the converse of \cref{lem:maybeeta} does not hold: 
there exists a term $t \in \maybeeta$
such that forall substitution $\rho$, $\rho t$ is not an
$\eta$-expansion. A simple counter example is
$\lambda x. f \appsep (A \appsep x) \appsep (A \appsep x)$
which is in \maybeeta{} since $x$ does not \occurrigid{} in the first argument
of $f$,
and the second argument of $f$ \reduceto{} $x$. In other words $A \appsep x$
may either use or discard $x$, but our analysis does not know that \emph{the same
term} cannot have two contrasting behaviors.\\
This is however not a problem in the sense that it does not break
\cref{prop:simulation}. Terms in \maybeeta{} are compiled to
unification variables and a link (see \cref{sec:etacomp}):
the link makes progress (see \cref{sec:etaprogress})
in the same step in which the
variable is instantiated, and that compensates for this coarse analysis.

>>>>

\noindent
Remark that the converse of \cref{lem:maybeeta} does not hold: 
there exists a term $t$ satisfying the criteria (1) above
that is not in $\maybeeta$, i.e.
there exists no substitution $\rho$ such that $\rho t$ is an
$\eta$-expansion. A simple counter example is
$\lambda x. f \appsep (A \appsep x) \appsep (A \appsep x)$
since $x$ does not \occurrigid{} in the first argument
of $f$,
and the second argument of $f$ \reduceto{} $x$.
In other words $A \appsep x$
may either use or discard $x$, but our analysis does not
take into account that \emph{the same
term} cannot have two contrasting behaviors.

As we will see in the rest of this section this is not a problem
since it does not break
\cref{prop:simulation} nor \cref{prop:fidelity}.
% A term in \maybeeta{} is compiled to a
% unification variable and a link (see \cref{sec:etacomp}):
% the link makes progress (see \cref{sec:etaprogress})
% in the same step in which the
% variable is instantiated, and that compensates
% for this coarse analysis.
